MCC Kids Model Predictions

### 2019-02-05 stats/kids/kids_model_predictions.Rmd
update repo for MH

pref_prior_con <- pref_prior_con%>%
  mutate(chain = factor(Chain),
         alignment = "congruent")

@@

## Model code for predictions

@@

@@

## Sampling predictions

Taking samples and munging the data.

model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
  data = pre_data,
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

```
## Sanity checks

@@

@@

## importing data
files <- dir("~/Work/MCC/git-mcc/kids_EX3/pref/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_EX3/pref/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,42,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

raw_data <- raw_data %>%
  mutate(subid = ifelse(subid == "181128_3_ex3p....","181128_3_ex3p" , subid),
         subid = ifelse(subid == "181128_1_ex3p.","181128_1_ex3p" , subid),
         subid = ifelse(subid == " 181218_10_ex3p","181218_10_ex3p" , subid))

raw_data%>%
  #group_by(paste(subid,test_date))%>%
  group_by(subid)%>%
  summarise(n= n())

unique(raw_data$subid)

log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "ex3p")%>%
  select(subid,experimenter,keep_drop,sex,dob)

#unique(log$subid)
sum(log$keep_drop == "drop")

d <- left_join(raw_data,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))

@@

p_data <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  mutate(age_bin = age_num - 3,
         Speaker = ifelse(speaker == "same", "same_speaker", "different_speaker"),
         Alignment = alignment)%>%
  group_by(Speaker, alignment ,age_bin, subid)

@@

data <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  mutate(Speaker = ifelse(speaker == "same", "same_speaker", "different_speaker"),
         Alignment = alignment)%>%
  group_by(Speaker, Alignment ,subage) %>%
  summarize(k = sum(correct_inf), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         Data_ci_lower  = qbeta(.025, a, b),
         Data_ci_upper = qbeta(.975, a, b),
         Data = (a-1)/(a+b-2))%>%
  select(-a,-b,-n,-k)

>>>>

pref_prior_con <- pref_prior_con%>%
  mutate(chain = factor(Chain),
         Alignment = "congruent")

@@

## Basic RSA model predictions

@@

# model_pred<- webppl(
#   program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
#   data = pre_data,
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 900, burn = 200, verbose = T)
# )

@@

## Prior only model

@@

```
# Sanity checks

# Visualizing model predictions

@@

## importing data
d <- read_csv(file="../data/kids_ex3_data.csv")

# files <- dir("~/Work/MCC/git-mcc/kids_EX3/pref/")
# 
# raw_data <- data_frame()
# for (f in files) {
#   jf <- paste("~/Work/MCC/git-mcc/kids_EX3/pref/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   date <- str_sub(jf,42,str_length(jf)-11)
#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
#   raw_data <- bind_rows(raw_data, id)
# }
# 
# raw_data <- raw_data %>%
#   mutate(subid = ifelse(subid == "181128_3_ex3p....","181128_3_ex3p" , subid),
#          subid = ifelse(subid == "181128_1_ex3p.","181128_1_ex3p" , subid),
#          subid = ifelse(subid == " 181218_10_ex3p","181218_10_ex3p" , subid))
# 
# raw_data%>%
#   #group_by(paste(subid,test_date))%>%
#   group_by(subid)%>%
#   summarise(n= n())
#   
# unique(raw_data$subid)
# 
# log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
#   filter(Condition == "ex3p")%>%
#   select(subid,experimenter,keep_drop,sex,dob)
# 
# #unique(log$subid)
# sum(log$keep_drop == "drop")
# 
# d <- left_join(raw_data,log, by = "subid")%>%
#   filter(keep_drop == "keep")%>%
#   mutate(dob = as.numeric(dob),
#          dob = as.Date(dob,origin = "1899-12-30"),
#          age_num = lubridate::time_length(difftime(test_date,dob), "years"),
#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
#          Speaker = ifelse(speaker == "same", "same_speaker", "different_speaker"),
#          Alignment = alignment)%>%
#   select(-speaker,-alignment)
# 
# 
# #write_csv(d, "../data/kids_ex3_data.csv")

@@

p_data <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  mutate(age_bin = age_num - 3)%>%
  group_by(Speaker, Alignment ,age_bin, subid)

@@

data <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(Speaker, Alignment ,subage) %>%
  summarize(k = sum(correct_inf), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         Data_ci_lower  = qbeta(.025, a, b),
         Data_ci_upper = qbeta(.975, a, b),
         Data = (a-1)/(a+b-2))%>%
  select(-a,-b,-n,-k)
